### 2020-04-29 README.Rmd
Add first pass for all cities

```{r}
roads = rsf %>% filter(region == "London", pctgov > 500)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.zoom.limits = c(12, 13)) + tm_scale_bar()
```

@@

```{r}
roads_top = roads %>%
  filter(length > 500) %>% 
  arrange(desc(pctgov)) %>%
  slice(1:10) 
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_view(set.zoom.limits = c(12, 13)) + tm_scale_bar()

@@

```{r}
roads = rsf %>% filter(region == "Cambridge", pctgov > 400)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_scale_bar()
```

@@

```{r}
roads_top = roads %>%
  filter(length > 100) %>% 
  arrange(desc(pctgov)) %>%
  slice(1:10) 
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_view(set.zoom.limits = c(14, 150)) + tm_scale_bar()

@@

>>>>

```{r}
roads = rsf %>% filter(region == "London", pctgov > 500)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.view = 11) + tm_scale_bar()
```

@@

```{r}
roads_top = roads %>%
  filter(length > 500) %>% 
  filter(!name == "Talgarth Road", length > 500) %>% 
  arrange(desc(pctgov)) %>%
  slice(1:10) 
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_view(set.view = 12) + tm_scale_bar()

# Birmingham

```{r}
roads = rsf %>% filter(region == "Birmingham", pctgov > 100)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.view = 12) + tm_scale_bar()
```

```{r}
roads_top = roads %>%
  filter(length > 300) %>% 
  arrange(desc(pctgov)) %>%
  slice(1:10) 
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_view(set.view = 13) + tm_scale_bar()

# Manchester

```{r}
roads = rsf %>% filter(region == "Manchester", pctgov > 100)
region_centre = tmaptools::geocode_OSM("Manchester", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 7000)
roads = st_intersection(roads, region_buff)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.view = 12) + tm_scale_bar()
```

```{r}
roads_top = roads %>%
  filter(length > 300) %>% 
  arrange(desc(pctgov)) %>%
  slice(1:10) 
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_view(set.view = 13) + tm_scale_bar()

@@

# Liverpool

```{r}
roads = rsf %>% filter(region == "Liverpool", pctgov > 100)
region_centre = tmaptools::geocode_OSM("Liverpool", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 9000)
roads = st_intersection(roads, region_buff)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.view = 12) + tm_scale_bar()
```

@@

```{r}
roads_top = roads %>%
  filter(length > 300) %>% 
  arrange(desc(pctgov)) %>%
  slice(1:10) 
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_view(set.view = 12) + tm_scale_bar()

@@

# Leicester

```{r}
roads = rsf %>% filter(region == "Leicester", pctgov > 100)
region_centre = tmaptools::geocode_OSM("Leicester", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 9000)
roads = st_intersection(roads, region_buff)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.view = 12) + tm_scale_bar()
```

```{r}
roads_top = roads %>%
  filter(length > 300) %>% 
  arrange(desc(pctgov)) %>%
  slice(1:10) 
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_view(set.view = 12) + tm_scale_bar()

# Sheffield

```{r}
roads = rsf %>% filter(region == "Sheffield", pctgov > 100)
region_centre = tmaptools::geocode_OSM("Sheffield", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 9000)
roads = st_intersection(roads, region_buff)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.view = 12) + tm_scale_bar()
```

```{r}
roads_top = roads %>%
  filter(length > 600) %>% 
  arrange(desc(pctgov)) %>%
  slice(1:10) 
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_view(set.view = 12) + tm_scale_bar()

# Newcastle

```{r}
roads = rsf %>% filter(region == "Newcastle", pctgov > 100)
region_centre = tmaptools::geocode_OSM("Newcastle", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 9000)
roads = st_intersection(roads, region_buff)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.view = 12) + tm_scale_bar()
```

```{r}
roads_top = roads %>%
  filter(length > 600) %>% 
  arrange(desc(pctgov)) %>%
  slice(1:10) 
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_view(set.view = 12) + tm_scale_bar()

```{r}
roads = rsf %>% filter(region == "Cambridge", pctgov > 400)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.view = 13) + tm_scale_bar()
```

```{r}
roads_top = roads %>%
  filter(length > 100) %>% 
  arrange(desc(pctgov)) %>%
  slice(1:10) 
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_view(set.view = 14) + tm_scale_bar()
